Analysis-ready VCF at Biobank scale using Zarr

### 2025-04-01 paper.tex
Added software heritage references and metadata

% 3. GitHub repository bio2zarr
% Project name:  bio2zarr
% Github link: https://github.com/sgkit-dev/bio2zarr/
% Python module: https://pypi.org/project/bio2zarr/
% Operating system(s): Platform independent
% Programming language: Python
% License: Apache-2.0
% Software Heritage PID: [207]

>>>>

\subsection{GitHub repository SAIGE-VCZ}
\begin{description}
\item[Project name:]  SAIGE-VCZ
\item[Github link:] \url{https://github.com/sgkit-dev/SAIGE-VCZ/}
\item[Operating system(s):] Platform independent
\item[Programming language:] C++, R
\item[License:] GPL-3.0
\item[Software Heritage PID:]
swh:1:snp:b868873e7e5dec417459cdf74de95647deb15167 \cite{saige-vcz-swh}
\end{description}

\subsection{GitHub repository vcztools}
\begin{description}
\item[Project name:]  vcztools
\item[Github link:] \url{https://github.com/sgkit-dev/vcztools/}
\item[Operating system(s):] Platform independent
\item[Programming language:] Python, C
\item[License:] Apache-2.0
\item[Software Heritage PID:] 
swh:1:snp:bdf1771ddb19144626df61a74cbe1e6fcdc634bc \cite{vcztools-swh}
\item[RRID:] SCR\_026482
\item[Bio.tools Unique Identifier:] vcztools
\end{description}
